%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    \cventry
        {Cloud Support Engineer}
        {Amazon Web Service}
        {Aug. 2019 - Present}
        {Taipei, Taiwan}
        {
            \begin{cvitems}
                \item
                    {
                        Being responsible for helping customers solve questions about container and deployment related AWS services, including:
                        \begin{itemize}
                            \item Amazon Elastic Container Service(Amazon ECS) 
                            \item Amazon Elastic Kubernetes Service (Amazon EKS)
                            \item AWS App Mesh(AWS hosted Envoy control plane)
                            \item AWS Code-series services(AWS CodeCommit, AWS CodeBuild, AWS CodeDeploy, AWS CodePipeline)
                            \item AWS Infrastructure as code services(AWS CloudFormation, AWS CDK) 
                            \item AWS X-Ray
                            \item AWS Batch
                        \end{itemize}
                    }
                \item
                    {
                        Providing wild range support skills to assist customers. For instance:
                        \begin{itemize}
                            \item Providing general guidance about a service's feature or use case. Sometime, providing prototype or writing sample code for customers is required.
                            \item Helping customer fix issues caused by mis-configuring.
                            \item Tracking issue and providing workaround/solutions when the problem which customer encounter is caused by AWS services or infrastructure. Sometimes, help AWS internal team trace services' or tools' source code is required.
                            \item Under some situation, problems are cause by network connectivity issue, OS performance issue, or open source projects' source code/configuration. Having wild range of different troubleshooting kills and knowledge is required.
                            \item To cooperate with customers to figure out their real problem and find most suitable solutions, great communication skill is required.
                        \end{itemize}
                    }
            \end{cvitems}
        }

    \cventry
        {Development Operator}
        {Bo-Ning Tech. Corp.}
        {Feb. 2017 - Aug. 2019}
        {Hsinchu, Taiwan}
        {
            \begin{cvitems}
                \item
                    {
                        Constructed CI/CD pipeline based on Drone.
                        \begin{itemize}
                            \item Containerized services for easier deploying and testing.
                            \item Integrated Drone and GitLab for testing.
                            \item Constructed Sonatype Nexus Repository as artifact repository.
                        \end{itemize}
                    }
                \item
                    {
                        Constructed monitoring system for services.
                        \begin{itemize}
                            \item Used Elastic Search and Fluented for collecting logs for services.
                            \item Used Kibana to visualize and generate statistic reports.
                            \item Hooked monitoring system with Slack for alarm.
                        \end{itemize}
                    }
                \item
                    {
                        Managed cloud infrastructure(GCP) and container cluster (Docker Swarm).
                    }
            \end{cvitems}
        }

    \cventry
        {Software Engineer}
        {IChen Corp.}
        {Taipei, Taiwan}
        {Sep. 2015 - Feb. 2017}
        {
            \begin{cvitems}
                \item
                    {
                        Constructed VoIP server for intercom system of parking lots based on FreeSwitch 1.6, and developed client on Raspberry Pi in Python and C-Language.
                    }
                \item
                    {
                        Designed self-service system for parking lots to allow customers parking vehicles and paying by license plates without human parking officers.
                        \begin{itemize}
                            \item Developed device-controlling framework to allow controlling RS-232-protocol-based devices by TCP/IP in python.
                            \item Developed automatic pay station based on PyQt5, device-controlling framework, and using RESTful API for uploading accounts.
                            \item Developed access management system based on device-controlling framework, using C\# to control third-party license plate recognition system, and uploading access information through RESTful API.
                        \end{itemize}
                    }
                \item 
                    {  
                        Designed self-service system for restaurants to allow customers ordering and paying without human receptionist.
                        \begin{itemize}
                            \item Developed automatic pay station based on Tkinter, device-controlling framework, and using RESTful API for uploading accounts. 
                        \end{itemize}
                    }
                \item
                    {
                        Managed infrastructures(GCP and OpenVPN) and CD-chain for account and CRM server for self-serve system for parking lots and restaurants.
                        \begin{itemize}
                            \item Constructed GitLab for source code control.
                            \item Wrote Ansible playbooks for deployment and management.
                        \end{itemize}
                    }
            \end{cvitems}
        }

    \cventry
        {Intern Software Engineer}
        {Leap Electronic Co., Ltd.}
        {Taipei, Taiwan}
        {May. 2014 - Sep. 2014}
        {
            \begin{cvitems}
                \item
                    {
                        Developed IC-burning driver by C-Language and assembly language for IC-burner produced by Leap.
                    }
                \item
                    {
                        Developed driver for Atmel-ATtiny45 and Atmel-AT89C51.
                    }
            \end{cvitems}
        }
        
    
    \cventry
        {Student Partner}
        {Microsoft Corp.}
        {Taipei, Taiwan}
        {Jun. 2013 - Sep. 2013}
        {
            \begin{cvitems}
                \item Developed Windows 8 Store Applications and Windows Phone 8 Applications by C\# and Blend.
                \item Gave speech of introducing Windows 8 to promote Windows 8 around universities in Taiwan.
            \end{cvitems}
        }

\end{cventries}
